A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-15 manuscript/reply_to_reviewers.tex

		\begin{quotation}
			Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig. 5C), indicating that the posterior webs include many more interactions between specialists than the observed network. In addition, the stronger the detection filter, the farther apart were the nestedness of the observed and posterior webs. This suggests that the interactions included in the observed network are not a random subset of those included in the posterior webs.
		\end{quotation}

\clearpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#3}
% ---------------------------------------

	The Reviewer commented that our paper is, overall, very good and ``makes an important contribution" as ``a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages". We are glad that the Reviewer agrees about the importance of this message and appreciate his/her suggestions to improve the manuscript. We have taken care to add references and clarify the introduction, as well as to state explicitly that we are emphaticallly not suggesting that anyone sample with lower effort/intensity than they otherwise would. We considered the benefits of high-quality sampling to be so self-evident that it did not occur to us that our manuscript could be read as suggesting that extensive sampling is not worthwhile. We thank the Reviewer for pointing out the potential for confusion over this point and hope that it is now clear that Bayesian analyses are a complement to, not a replacement for, high-quality sampling. Below we adress each of the Reviewer's suggestions in detail.

@@

	1. Add more references to the literature [[done]]

		\begin{refquote}
		1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realize that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for stressing the need to further acknowledge previous work in the field. As this was also emphasized by other reviewers, we have taken this carefully \emph{ad notam} and expanded our references to earlier work as much as possible given length restrictions. We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors. We hope that the introduction now presents a more thorough sample of previous work.

@@

		\begin{refquote}
		Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation. 
		\end{refquote}

		\textbf{R:} We agree with the Reviewer regarding our intended meaning, and have modified this accordingly:

@@

			\begin{quotation}
				Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
			\end{quotation}

		\begin{refquote}
		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\
		\end{refquote}

			\textbf{R:} We agree, and have added a citation to Bartomeus as requested. In terms of why we will have omitted references to other similar papers and to some less conceptual and empirical attempts, we must stress that we are not striving for a comprehensive review but rather trying to reach a particular audience with a particular message, for which we find MEE the ideal forum. The length and formatting constraints of an MEE article mean that, for the sake of brevity and clarity, we cannot cite all previous work concerning detection probability.

@@

		\begin{refquote}
			Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
		\end{refquote}

		\textbf{R:} We have rephrased the end of this paragraph to mention previous predictive models dealing with uncertainty in interaction matrices. As said, we have done our best to improve our coverage of previous work, within the limits offered by the current format.

@@

 			To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details). 
      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together. Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
      We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).

		\end{quotation}

	4. Misunderstanding of our point about sampling effort [[done]]

		\textbf{R:} We believe that the Reviewer has  misunderstood the point of our comments on sampling effort. Several of their comments suggest that we are advocating for reducing sampling effort. This is emphatically not the case. Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful. We now address this assumption explicitly in an appendix (Appendix S2)  dedicated to the potential for sampling effort to reduce uncertainty about interactions. Below, we address the Reviewer's sampling-related comments one by one.

@@

		\begin{refquote}
		Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me. 
		\end{refquote}

		\textbf{R:} Of course sampling more does not lead to less understanding. It can, however, reveal knowledge gaps (as when a rare species is detected, revealing our ignorance of its interactions). This is not an argument against multiple sampling but a statement that increased sampling is likely to lead to the addition of more "false zeros" as species about which we know little are added to the network.

		\begin{refquote}
		Line 107.  There is a lot of literature in wildlife ecology emphasizing the importance of repeat sampling for estimating detection probability.  Is this just wrong?  If so this does need more explanation in the context of this literature.
		\end{refquote}

		\textbf{R:} Here it seems that we have expressed ourselves poorly. Of course we are not against repeat sampling. This is, in fact, one of the core parts of our approach. Our point here is that some species (e.g., cryptic or difficult-to-identify species) and interactions (e.g., brief visits of pollinators to plants) are difficult to detect and may be missed even with multiple sampling. If a rare species is only detected in one sampling round, then the repeated sampling necessarily tells us little about its interactions. For species which are frequently detected, we absolutely learn about the detection probability of their interactions with repeated sampling. We have tried to clarify our intended meaning throughout the revised text.

@@

		\begin{refquote}
		Line 130.  The ideas here are largely a repeat from those above.  Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?  I wonder if the argument is a bit more statistical than biological.
		\end{refquote}

		\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, and again we regret the confusion caused by our previous draft. We argue only that the amount of sampling required to be confident that co-occurring species do not interact is large -- likely beyond what is feasible for speciose systems given the limited resources available to many researchers. Sampling across most network studies is almost certainly not sufficient, but data which would allow readers to judge this (i.e., number of times each species is observed, independent of numbers of observed interactions) is not generally provided. Overall, we assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources. Infinite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.

@@

		\begin{refquote}
		Line 319.  It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?  Should this be made clear?  Otherwise, we maybe can just never get enough data!
		\end{refquote}

		\textbf{R:} We are specifically speaking about interactions which were never observed. As interaction networks tend to be sparse, there will always be many of these. If interaction frequencies were higher among species that co-occurred, then we would have fewer unobserved interactions but the sample sizes needed to be confident that an unobserved interaction does not occur would not change (perhaps our threshold for deciding to believe a zero might, which is why we provide sample sizes for several thresholds). The Reviewer has hit the nail on the head with the idea that it is extremely hard to get enough data to be sure about every interaction. This is why prior knowledge can be so useful!

		\begin{refquote}
		Line 338 to 342.  Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
		\end{refquote}

		\textbf{R:} In our revised manuscript, we have collected our discussion of sampling into a dedicated appendix and added several explicit statements that high-quality sampling can reduce some sources of uncertainty. We hope that it is now clear that sampling is very important but cannot completely eliminate uncertainty (except perhaps in some very species-poor and unusually static systems, but these are certainly rare). As to adding more zeros than ones specifically, this is only "bad" in the sense that it gives us more high-uncertainty cells in the interaction matrix. We take the view that it is better to have "known unknowns" than "unknown unknowns" and it is certainly better to know about more of the species in a community than fewer, but finding a single individual of a rare species will not reduce uncertainty in the web. We have added a line (XX-XX) specifically to address this.

@@

			\end{quotation}

	7. Why not always model probabilities of co-occurrence? [[done]]

		\begin{refquote}
		Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
		\end{refquote}

		\textbf{R:} Modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}). In some systems, however, the factors affecting probabilities of co-occurrence may not be known. We therefore cannot suggest modelling co-occurrence as a panacea. Instead, we now emphasize that co-occurrence probabilities are one thing that could be included in a prior (lines XX-XX - section Informative priors). 
		\smallskip
		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift). Following the Reviewer's suggestion, we have revised our manuscript to clarify our technology. In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript. We hope that this will remove some of the confusion about whether or not modelling different components of uncertainty/sampling more is a good idea.

@@

	8. Issue of testing hypotheses based on inputs into models [[done]]

		\begin{refquote}
		Line 121.  I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realize there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?
		\end{refquote}

		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out). We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines XX-XX). We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.

@@

		\begin{quotation}
			Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. 
		\end{quotation}

	11. Skepticism about sampling requirements to be sure interactions do not occur [[done]]

		\begin{refquote}
		Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialized or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed…. This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed…??
		\end{refquote}

		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed. Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur. Given this, we do not think that recommending uncertainty be explicitly stated undermines our point.

		The Reviewer's suggestion that we might need fewer samples for species that are "specialized or bound to interact for some other reason" reflects a very strong prior. In this case, yes we would need fewer samples for the species concerned. With sufficiently strong priors, it is not necessary to sample at all! For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros. In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are "bound to interact" (or not to interact). The concept of pollination syndromes is one example - many flower visitors are less rigidly specialized on particular flower types than initially thought~\citep{Ollerton2009}. To address such "forbidden links", we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros. This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes. We hope that this expanded recommendation (lines XX-XX) is clearer.

@@

		\end{quotation}

\clearpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#4}
% ---------------------------------------

	[[Still need to incorporate Tomas comments]]
	[[Still need to spellcheck]]

	The Reviewer has ``been surprised how little that sampling effects have been formally considered in the analysis of networks" and therefore feels that our manuscript makes an important contribution. Nevertheless, the Reviewer has concerns that the manuscript might not reach empirical ecologists ``because they either would not understand its relevance or would not be able to apply it practically". We agree with the Reviewer that this would be a great shame, and appreciate their suggestions to improve the manuscript. With this revision, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it. Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.

@@

		\textbf{R:} We have revised the manuscript with an eye to clarifying the flow between sections. We hope that it is now clear that our proposed framework is designed to use Bayesian theory to complement empirical networks and empiricists' detailed knowledge of their systems.

	2. Add more citations [[done]]

		\begin{refquote}
		Introduction – T. Poisot and colleagues have done a lot of relevant work in this area, but I felt there was undue reference to their work in comparison with other relevant work. There were some obvious papers (e.g. sampling by Jordano, forbidden links by various others) that were not cited. A broader perspective on the literature would, I think, help the authors appreciate the value of their paper and the need to ensure that it is fully understandable and of practical use.
		\end{refquote}

		\textbf{R:} All of the Reviewers were unhappy with our treatment of the literature, and we have now done our best to improve on this, bearing in mind the strict word limit of MEE and the fact that it was never our goal to conduct a comprehensive review. We have cited additional literature as recommended by Reviewer 1, including a paper by Jordano. If the Reviewer has any suggestions of specific papers that they feel are missing, we would be happy to consider them as well. Note, however, that we do not intend our manuscript to be a complete review of the literature surrounding interaction probabilities. We hope that the citations we have added appear more balanced to the Reviewer.

@@

	3. Comment on weighted metrics [[done]]

		\begin{refquote}
		L36ff The authors should note the value of weighted metrics in taking account of sampling biases.
		\end{refquote}

		\textbf{R:} We do not see how weighted metrics (which we infer mean metrics including interaction strength/frequencies based on the Reviewer's comment below) account for sampling biases. It seems to us that measures of interaction strength should be \emph{more} susceptible to sampling biases, not less, as abundant species are both more likely to have their interactions recorded and more likely to have these interactions recorded as strong/frequent. Of course weighted metrics have many other strengths, but these are not germane to the topic at hand. We have rephrased the introduction so that the original line 36 no longer appears, and hope that this will remove the Reviewer's objection.

	4. Request for extension to weighted networks [[not done - do we want to do this?]]

@@

		\begin{refquote}
		L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.
		\end{refquote}

		\textbf{R:} As stated above, we do not agree that weighted networks reduce sampling biases. Moreover, we disagree that it is rare to use binary networks as most food webs (for example) are still binary. It takes an even greater sampling effort to quantify interaction strengths than the presence and absence of links, so for species-rich systems in particular there simply are not many high-quality weighted networks published. Moreover, as the Reviewer mentioned, empirical ecologists may already struggle to apply a Bayesian framework using qualitative data. We therefore opted not to extend our framework in this manuscript and leave this as an area for future work.

@@

	5. Description of causes of uncertainty poorly integrated with the case study [[done]]

		\begin{refquote}
		L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
		Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. 
		\end{refquote}

		\textbf{R:} As we state in the section \textbf{Estimating uncertainty}, we usually cannot distinguish different sources of uncertainty in empirical data. Those studies which attempt to do so (e.g.,~\citet{Graham2018}) remove process uncertainty by assuming constant interaction probabilities during a short, intense sampling period and also assume that we know the true set of feasible interactions. This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc.

### 2019-01-15 manuscript/CI_interactions.tex
spellcheck UK english

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

@@

    To sum up, the absence of an interaction on a given day could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

@@

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:

@@

    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}). The influence of the prior on the posterior distribution can be understood from these definitions: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$. In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and more on the observed data. As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}). Note that these Bayesian models of $\lambda_{ij}$ do not distinguish between different sources of uncertainty except through the choice of prior.

@@

        In most cases, we have some prior knowledge which we can use to inform uncertainty about interactions. One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truldy do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,Graham2018}. Using an informative prior like these tailors the level of uncertainty surrounding each interaction, but involves many assumptions. There is, therefore, a risk of over-fitting with complicated trait-based models. Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).

@@

        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Spiegelhalter2000}. This approach is used in medical testing~\citep{Spiegelhalter2000} and disease modelling~\citep{Leyland2005} using information from pilot studies and can easily be applied to ecological systems. Returning to the example of degree distributions, approximate Bayes allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely. Despite its practicality, approximate Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}. We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data. Nevertheless, there are likely to be many situations where approximate Bayes provides the best way to describe the uncertainty in the dataset. We therefore illustrate this approach in the following empirical example.

@@

        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information. As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution. This simulates an empirical Bayes model using a pilot site to inform the prior distribution. A site in the middle of the geographic distribution was chosed in order to minimize bias due to the potential for a northern or southern site to exclude species with restricted ranges. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller system, which provided unreasonable distributions for interaction probabilites (\emph{Appendix S7}).

>>>>

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

@@

    To sum up, the absence of an interaction on a given day could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$]. Note that some external factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

@@

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:

@@

    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}). The influence of the prior on the posterior distribution can be understood from these definitions: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$. In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and more on the observed data. As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}). Note that these Bayesian models of $\lambda_{ij}$ do not distinguish between different sources of uncertainty except through the choice of prior.

@@

        In most cases, we have some prior knowledge which we can use to inform uncertainty about interactions. One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,Graham2018}. Using an informative prior like these tailors the level of uncertainty surrounding each interaction, but involves many assumptions. There is, therefore, a risk of over-fitting with complicated trait-based models. Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).

@@

        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Spiegelhalter2000}. This approach is used in medical testing~\citep{Spiegelhalter2000} and disease modelling~\citep{Leyland2005} using information from pilot studies and can easily be applied to ecological systems. Returning to the example of degree distributions, approximate Bayes allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely. Despite its practicality, approximate Bayes has been criticised for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}. We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data. Nevertheless, there are likely to be many situations where approximate Bayes provides the best way to describe the uncertainty in the dataset. We therefore illustrate this approach in the following empirical example.

@@

        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information. As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution. This simulates an empirical Bayes model using a pilot site to inform the prior distribution. A site in the middle of the geographic distribution was chosen in order to minimise bias due to the potential for a northern or southern site to exclude species with restricted ranges. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller system, which provided unreasonable distributions for interaction probabilities (\emph{Appendix S7}).
